### 2020-01-31 wuhan.tex
fiddle
Trying to resolve and/or comment out comments.

\jd{The pictures with linear scale for Ro (and r) are fine, and the Ro ones look similar. But I would say that it's a good principle to use log scales for things like Ro and r, where it's more or less clear that the important distances are multiplicative.}
\jd{I have no problem doing this in the next round, though. Time is important.}
\fref{eff} shows how propagating uncertainty ($\mu_r$, $\mu_G$, and $\mu_\kappa$) in different combinations would affect estimates and CIs for \Ro. For illustrative purposes, we use our pooled estimates, which represent a reasonable proxy for the state of knowledge as of 26 January. 
Propagating error from the growth rate (which all but one of the models did) is absolutely crucial:
\jd{I really dislike these in-text numbers, plus it misses the point that the cruciality of them depends primarily on something else (the comparison of things that leave them out with the last two bars). Who wanted this and why? I can write something about the comparison above instead?}.
uncertainty on \Ro, measured with our 95\% CI, is more than two fold in this case (95\% CI: 2.22--5.16).
Propagating error from the generation interval also has important effects, however (95\% CI: 2.59--4.12).
Once these two are included, the impact of leaving out uncertainty in the dispersion would be small, in this particular example -- 
propagating errors from $r$ and $\bar G$ gives 95\% CI of 2.16--5.58 whereas propagating all errors gives 95\% CI of 2.06--5.89 (compare \textbf{growth rate + GI mean} with \textbf{all} in \fref{eff}).

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure2.pdf}
\caption{
\textbf{Effects of $r$, $\bar G$, and $\kappa$ on the estimates of \Ro.}
We compare estimates of \Ro under five scenarios that propagate different combinations of uncertainties.
\textbf{base}: \Ro estimates based on the median estimates of $\mu_r$, $\mu_G$, and $\mu_\kappa$.
\textbf{growth rate}: \Ro estimates based on the the posterior distribution of $\mu_r$ while using median estimates of $\mu_G$ and $\mu_\kappa$.
\textbf{GI mean}: \Ro estimates based on the the posterior distribution of $\mu_G$ while using median estimates of $\mu_r$ and $\mu_\kappa$.
\textbf{growth rate + GI mean}: \Ro estimates based on the the joint posterior distributions of $\mu_r$ and $\mu_G$ while using a median estimate of $\mu_\kappa$.
\textbf{all}: \Ro estimates based on the joint posterior distributions of  $\mu_r$, $\mu_G$, and $\mu_\kappa$.
Vertical lines represent the 95\% confidence intervals.
\jsw{why not show all combinations}
}
\label{fig:eff}
\end{figure}

@@

Here, we only focused on estimates of \Ro that were published within a very short frame of time.
Although our analysis reflects a snapshot of a fast moving epidemic, our lessons will hold: understanding uncertainties in generation-interval distribution is important.
As the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will inevitably decrease, 
and the effect of uncertainty in the mean generation time will become more important.
A recent epidemiological analysis of the patient-level data revealed large uncertainty in serial intervals, which is defined as the time between symptom onsets of an infector and an infectee, (mean: 7.5 days; 95\% CI: .3--19) \citep{nejmncov};

>>>>

%% \jd{The pictures with linear scale for Ro (and r) are fine, and the Ro ones look similar. But I would say that it's a good principle to use log scales for things like Ro and r, where it's more or less clear that the important distances are multiplicative.}
%% \jd{I have no problem doing this in the next round, though. Time is important.}
\fref{eff} shows how propagating uncertainty ($\mu_r$, $\mu_G$, and $\mu_\kappa$) in different combinations would affect estimates and CIs for \Ro. For illustrative purposes, we use our pooled estimates, which represent a reasonable proxy for the state of knowledge as of 26 January. 
Comparing the models that include only some sources of uncertainty to the confidences intervals from the ``all'' model, we see that propagating error from the growth rate (which all but one of the models did) is absolutely crucial: the middle bar, which lacks growth-rate uncertainty is far too narrow.
%% \jd{I really dislike these in-text numbers, plus it misses the point that the cruciality of them depends primarily on something else (the comparison of things that leave them out with the last two bars). Who wanted this and why? I can write something about the comparison above instead?}.
%% uncertainty on \Ro, measured with our 95\% CI, is more than two fold in this case (95\% CI: 2.22--5.16).
Propagating error from the generation interval also has important effects. 
%% however (95\% CI: 2.59--4.12).
Once these two are included, the impact of leaving out uncertainty in the dispersion is small, though noticeable, in this particular example.
%% -- propagating errors from $r$ and $\bar G$ gives 95\% CI of 2.16--5.58 whereas propagating all errors gives 95\% CI of 2.06--5.89 (compare \textbf{growth rate + GI mean} with \textbf{all} in \fref{eff}).

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure2.pdf}
\caption{
\textbf{Effects of $r$, $\bar G$, and $\kappa$ on the estimates of \Ro.}
We compare estimates of \Ro under five scenarios that propagate different combinations of uncertainties.
\textbf{base}: \Ro estimates based on the median estimates of $\mu_r$, $\mu_G$, and $\mu_\kappa$.
\textbf{growth rate}: \Ro estimates based on the the posterior distribution of $\mu_r$ while using median estimates of $\mu_G$ and $\mu_\kappa$.
\textbf{GI mean}: \Ro estimates based on the the posterior distribution of $\mu_G$ while using median estimates of $\mu_r$ and $\mu_\kappa$.
\textbf{growth rate + GI mean}: \Ro estimates based on the the joint posterior distributions of $\mu_r$ and $\mu_G$ while using a median estimate of $\mu_\kappa$.
\textbf{all}: \Ro estimates based on the joint posterior distributions of  $\mu_r$, $\mu_G$, and $\mu_\kappa$.
Vertical lines represent the 95\% confidence intervals.
%% \jsw{why not show all combinations}
%% {We discussed this, but came down on the side of simplicity. There are no examples I can think of where people included uncertainty in κ but left out one of the two big ones.}
}
\label{fig:eff}
\end{figure}

@@

Here, we only focused on estimates of \Ro that were published within a very short frame of time.
Although our analysis reflects a snapshot of a fast moving epidemic, our lessons will hold: uncertainties in generation-interval distribution is important.
As the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will eventually decrease, 
and the effect of uncertainty in the mean generation time will become more important.
